Unveiling Toronto's Respiratory Landscape

### 2024-01-25 outputs/paper/paper.qmd
Update paper.qmd

---
title: "Unveiling Toronto's Respiratory Landscape"
subtitle: "Analyzing Post-COVID-19 Infection Trajectory and Rhinovirus Surges through 2020 and 2023 Datasets"
author: 
  - Hailey Jang
thanks: "Code and data supporting this analysis is available at: "https://github.com/Hailey-Jang/PostCOVID_Respiratory_Problems.git"
date: January 23, 2024
date-format: long
abstract: "This research investigates the impact of COVID-19 on respiratory infections in Toronto, utilizing datasets from 2020 and 2023. Through analysis of simulated data on respiratory infection rates, with a focus on Rhinovirus, a noticeable surge in respiratory ailments post-pandemic is revealed. Statistical examinations comparing infection rates offer insights into the changing dynamics of respiratory health in the city. This study contributes valuable information towards understanding the lasting effects of COVID-19 on respiratory well-being in the Toronto population, providing a crucial foundation for public health strategies and interventions."
output: pdf_document
number-sections: true
format: pdf
bibliography: references.bib
---

>>>>

---
title: "Unveiling Toronto's Respiratory Landscape"
subtitle: "Analyzing Post-COVID-19 Infection Trajectory and Rhinovirus Surges through 2020 and 2023 Datasets"
author: 
  - Hailey Jang
thanks: "Code and data supporting this analysis is available at: https://github.com/Hailey-Jang/PostCOVID_Respiratory_Problems.git"
date: January 23, 2024
date-format: long
abstract: "This research investigates the impact of COVID-19 on respiratory infections in Toronto, utilizing datasets from 2020 and 2023. Through analysis of simulated data on respiratory infection rates, with a focus on Rhinovirus, a noticeable surge in respiratory ailments post-pandemic is revealed. Statistical examinations comparing infection rates offer insights into the changing dynamics of respiratory health in the city. This study contributes valuable information towards understanding the lasting effects of COVID-19 on respiratory well-being in the Toronto population, providing a crucial foundation for public health strategies and interventions."
output: pdf_document
number-sections: true
format: pdf
bibliography: references.bib
---
